An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-17 VLDB2026/main.tex
1

	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}

>>>>

	\textit{\textbf{ \textcolor{orange}{Search peak memory.}}}
	 \textcolor{orange}{As shown in Figure~\ref{fig:search_memory_mb_comparison}, we can find that the peak memory usage of each algorithm during search does not differ significantly. Among them, CAPS and NHQ have relatively higher peak memory usage, while the database's peak memory usage is comparatively lower.}
